Stack Safety as a Security Property

### 2020-07-09 main.tex
wip

\leo{Took a stab. Needs rewriting}%

After formally defining stack safety, we show that our definition is
enforceable using an existing tag-based enforcement
mechanism~\citep{DBLP:conf/sp/RoesslerD18}. We first consider their
conservative Depth Isolation policy, which not only enforces the
our formal definition of stack safety, but also a much stronger
property that requires integrity and confidentiality at every step of
an execution trace. This property is provably (in Coq)\leo{How to
  mention this?} stronger and stemmed out of the need to more
efficiently test stack safety. However, at the same time the
conservative enforcement mechanism is expensive to implement. In the
same work, \citeauthor{DBLP:conf/sp/RoesslerD18} propose a different
mechanism that is more efficient by virtue of being lazy in its
enforcement. At a high level, instead of guaranteeing integrity and
confidentiality when a callee returns, they check it when the caller
actually makes use of (potentially compromised) data. Thus, they
enforce a (also provably in Coq) weaker property that still protects
from unsafe callees, but is much less intuitive.

In summary, we offer the following contributions:\bcp{I would still like to
  see these points phrased in ``contribution normal form'': say exactly what
  we did for each one (it's a bit vague---''considers,'' etc.), and
  explicitly say why it is (a) useful, (b) challenging, and (c) novel.}
\begin{itemize}
\item
  % \leo{More? Extensional}\bcp{We might need to invent a word for   this---''quasi-extensional''?}
  Abstract formal properties capturing the
  intuitive concepts of strict local state encapsulation and well-bracketed
  control flow~(\cref{sec:lse-and-wbcf}) in a generic setting. These properties
  rule out common examples of stack memory abuse.
\item
  A case study of the Depth Isolation policy of \citet{DBLP:conf/sp/RoesslerD18}, based on hardware tags~(\cref{sec:enforcement}).
  This policy enforces our strict stack safety property, and also a (provably in Coq) stronger property that is easier to test.
  \apt{If we have no testing, do we even want to talk about the testing
    property?} \bcp{Not here; just in future work.  I guess we need to see
    whether we wind up with any results at all about testing.}
\item
  A refinement of the case study that considers the more efficient Lazy Tagging and Clearing policy
  of \citet{DBLP:conf/sp/RoesslerD18}~(\cref{sec:lazy}).  This policy does not enforce our strict
  local state encapsulation property,
  but a modified version of it using unique per-activation tags enforces
  an (also provably) weaker lazy variant of the property, which still prohibits
  the same intuitively stack unsafe behaviors.
%
% \apt{Awkward, but the truth I fear.} \bcp{I agree the phrasing is awkward,
%   but the point we can make is still strong: To make the property easier
%   to enforce, we can slightly weaken its guarantees; the weaker version is
%   a bit more complicated to state but still retains the pragmatic
%%   protections of the original.}\apt{To clarify: Nick's LT\&C policy uses
%   depth-based tags, which do not enforce even our lazy policy. So we need to
%   introduce a version of LT\&C that uses unique activation tags.}

@@

Enforcement mechanisms are modeled as {\em policies} that add some auxiliary
policy state to the ordinary machine state\bcp{This may be surprising to
  people who are not thinking about micropolicies.} and a partial policy
step function that
refines the machine step function by allowing or disallowing a step to be taken
based on its auxiliary state. This model will be made more precise in
\cref{sec:prelim}. It is flexible enough to capture any kind of mechanism used
for dynamic enforcement of properties of interest, including the following
representative families of policies.

>>>>

\bcp{This little paragraph is our entire explanation of the second and third
contributions!  Needs to be expanded considerably...}%
To provide evidence that our definitions capture the inituitive notion
of stack safety, we show that they rule out a range of exploitable bad
behaviors.\apt{``from the literature''??}  To assess whether they are
implementable, we compare them against
%proposed capability-based
%enforcement mechanism of \citet{Skorstengaard+19} \apt{we really
%  should} and
the existing tag-based enforcement mechanism of
\citet{DBLP:conf/sp/RoesslerD18}.
%\leo{Is this where we would rephrase this because we would only talk about it in related work?}

In summary, we offer the following contributions:\bcp{I would still like to
  see these points phrased in ``contribution normal form'': say exactly what
  we did for each one (it's a bit vague---''considers,'' etc.), and
  explicitly say why it is (a) useful, (b) challenging, and (c) novel.}
\begin{itemize}
\item
  % \leo{More? Extensional}\bcp{We might need to invent a word for   this---''quasi-extensional''?}
  Abstract formal properties capturing the
  intuitive concepts of strict local state encapsulation and well-bracketed
  control flow~(\cref{sec:lse-and-wbcf}) in a generic setting. These properties
  rule out common examples of stack memory abuse.
\item
  A case study of the Depth Isolation policy of \citet{DBLP:conf/sp/RoesslerD18}, based on hardware tags~(\cref{sec:enforcement}).
  This policy enforces our strict stack safety property, and also a (provably) stronger property that is easier to test.
  \apt{If we have no testing, do we even want to talk about the testing
    property?} \bcp{Not here; just in future work.  I guess we need to see
    whether we wind up with any results at all about testing.}
\item
  A refinement of the case study that considers the more efficient Lazy Tagging and Clearing policy
  of \citet{DBLP:conf/sp/RoesslerD18}~(\cref{sec:lazy}).  This policy does not enforce our strict
  local state encapsulation property,
  but a modified version of it using unique per-activation tags enforces
  a (provably) weaker lazy variant of the property.
%
% \apt{Awkward, but the truth I fear.} \bcp{I agree the phrasing is awkward,
%   but the point we can make is still strong: To make the property easier
%   to enforce, we can slightly weaken its guarantees; the weaker version is
%   a bit more complicated to state but still retains the pragmatic
%%   protections of the original.}\apt{To clarify: Nick's LT\&C policy uses
%   depth-based tags, which do not enforce even our lazy policy. So we need to
%   introduce a version of LT\&C that uses unique activation tags.}

@@

Enforcement mechanisms are modeled as {\em policies} that add some auxiliary
policy state to the ordinary machine state\bcp{This may be surprising to
  people who are not thinking about micropolicies.\apt{added para below}} and a partial policy
step function that
refines the machine step function by allowing or disallowing a step to be taken
based on its auxiliary state. This model will be made more precise in
\cref{sec:prelim}. It is flexible enough to capture any kind of mechanism used
for dynamic enforcement of properties of interest, including the following
representative families of policies.

We model ordinary program state and policy enforcement state separately to make it 
easier to use well-established concepts from language-based security.  
In particular, confidentiality has an elegant extensional characterization in terms of
\emph{noninterference}: a program preserves the confidentiality of certain data if
\emph{varying} that data would not change the program's observable behavior~\cite{??}.
In applying this idea to a system that incorporates policy enforcement, only
ordinary program data should be varied, whereas any associated policy enforcement
state should be left alone; our model makes this distinction obvious.
%That is, we compare the actual execution of the program with a \emph{hypothetical}
%execution where data has been varied. 
We also introduce a notion of observational integrity that relies on the idea of
\emph{rolling back} program state; again, our model makes it easy to describe
rollback of ordinary program data while leaving policy enforcement data unchanged.
